---
title: "Homework 6"
author: "Jason Maddox"
date: "5/2/2019"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(plyr)
library(tidyverse)
library(magrittr)
library(resample)
```

1. \textbf{Nonparametric Bootstrap CIs.}
(a) Bootstrap interval.
```{r}
boot_pct_ci <- function(x, conf = .95, B = 1e3) { 
  boot_means <- rerun(B, {
    sample(x, length(x), replace = TRUE) %>% 
    mean()
  })
  boot_means %>% 
    flatten_dbl() %>% 
    quantile(c((1 - conf) / 2, (1 + conf) / 2), names = FALSE)
}
set.seed(1)
(data <- rnorm(20, mean = 5, sd = 3) %>% round(2))
data %>% boot_pct_ci() %>% round(2)
```

(b) \textit{t}-interval.
```{r}
t_ci <- function(x, conf = .95) {
  c(mean(x) + qt((1 - conf)/2, length(x) - 1)*sd(x)/sqrt(length(x)),
    mean(x) - qt((1 - conf)/2, length(x) - 1)*sd(x)/sqrt(length(x)))
}
data %>% t_ci() %>% round(2)
data %>% t.test() %>% pluck("conf.int") %>% round(2)
```

(c) Bias corrected and adjusted bootstrap interval.
```{r}
boot_bca_ci <- function(x, conf = .95, B = 1e4) {
  bootstrap(x, mean, R = B) %>% 
    CI.bca(probs = c((1 - conf)/2, (1 + conf)/2), names = FALSE) %>% as.vector()
}
data %>% boot_bca_ci() %>% round(2)
```

(d) Simulation study.
```{r, cache = TRUE}
cover <- function(method) {
  ci <- rweibull(250, .2, 5) %>% method()
  ci[1] < 600 & ci[2] > 600
}
covs <- rerun(10000, {
  list(boot_pct_ci, t_ci, boot_bca_ci) %>% 
    map(cover) %>% 
    flatten_lgl()
}) %>% ldply()
covs %>% summarize(nonpar_btstrp = mean(V1), t = mean(V2), BCa = mean(V3))
```

2. \textbf{Parametric and Smooth Bootstrap.}
(a) Kernel density estimate.
```{r}
kdefun <- function(x) {
  kde <- (x %>% density())[c('x', 'y')] %>% transpose() %>% ldply(as_tibble)
  approxfun(kde$x, kde$y, yleft = 0, yright = 0)
}
```

(b) Plot kernel density estimate.
```{r}
ggplot(tibble(x = c(-4, 14)), aes(x)) +
  stat_function(fun = kdefun(data))
```

(c) Integrate KDE.
```{r}
integrate(kdefun(data), -Inf, Inf)
```

(d) Empirical CDF.
```{r}
ecdf2 <- function(x) {
  function(vals) {
    vals %>% map_dbl(~ mean(.x >= x))
  }
}
s <- seq(.5, 2.5, .5)
ecdf(1:2)(s)
ecdf2(1:2)(s)
```

(e) Smoothed empirical CDF.
```{r}
secdf <- function(x) {
  function(vals) {
    vals %>% map_dbl(~ integrate(kdefun(x), lower = -Inf, upper = .x)$value)
  }
}
pnorm(-3:3) %>% round(4)
secdf(rnorm(1e6))(-3:3) %>% round(4)
```

(f) Graph of CDFs.
```{r, cache = TRUE}
ggplot(tibble(x = c(-4, 14)), aes(x)) +
  stat_function(fun = pnorm, 
                args = list(mean = mean(data), sd = sd(data)), 
                aes(color = "green3")) +
  stat_function(fun = ecdf2(data), aes(color = "blue")) +
  stat_function(fun = secdf(data), aes(color = "red")) +
  scale_color_manual(name = "Estimated CDF", 
                     values = c("red" = "red", 
                                "blue" = "blue", 
                                "green3" = "green3"),
                     labels = c(expression(hat(F)[n](x)), 
                                expression(hat(F)[hat(theta)](x)), 
                                expression(hat(F)[S](x)))) +
  ylab(expression(hat(F)(x)))
```

(g) Parametric bootstrap.
```{r, cache = TRUE}
boot_param_ci <- function(x, conf = .95, B = 1e3) {
  boot_means <- rerun(B, {
    rnorm(length(x), mean(x), sd(x)) %>%
    mean()
  })
  boot_means %>% 
    flatten_dbl() %>% 
    quantile(c((1 - conf) / 2, (1 + conf) / 2), names = FALSE)
}
data %>% boot_param_ci() %>% round(2)
```

(h) Smooth bootstrap.
```{r, cache = TRUE}
boot_smooth_ci <- function(x, conf = .95, B = 1e3) { 
  boot_means <- rerun(B, {
    (sample(x, length(x), replace = TRUE) + rnorm(length(x), 0, bw.nrd0(x))) %>% 
    mean()
  })
  boot_means %>% 
    flatten_dbl() %>% 
    quantile(c((1 - conf) / 2, (1 + conf) / 2), names = FALSE)
}
data %>% boot_smooth_ci() %>% round(2)
```

(i) Simulation study.
```{r, cache = TRUE}
covs <- rerun(10000, {
  list(boot_pct_ci,
       t_ci,
       boot_bca_ci,
       boot_param_ci,
       boot_smooth_ci) %>% 
    map(cover) %>% 
    flatten_lgl()
}) %>% ldply()
covs %>% summarize(nonpar_btstrp = mean(V1), 
                   t = mean(V2), 
                   BCa = mean(V3),
                   par_btstrp = mean(V4),
                   smooth_btstrp = mean(V5))
```